---
title: "Instacart Dashboard"
output:
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
---

Here's a direct link to Aaki's homework 4 repository: https://github.com/ag2965/p8105_hw4_ag2965

The instacart dataset was used for this dashboard.

```{r setup, include=FALSE}
library(tidyverse)
library(p8105.datasets)
library(flexdashboard)
library(plotly)
```

Column {data-width=650}
-----------------------------------------------------------------------

### Chart A - Scatterplot

Chart A contains a scatterplot looking at the frequency of orders of the top 1000 most-ordered items. The aisles in which these order originate are color coded based on the legend on the right.
```{r}
data("instacart")

instacart = 
  instacart %>% 
  as_tibble(instacart)

instacart%>%
  janitor::clean_names()%>%
  group_by(aisle)%>%
  count(product_name)%>%
  filter(n>1000)%>%
plot_ly(
    x = ~product_name, y = ~n, type = "scatter", mode = "markers",
    color = ~aisle, alpha = 0.5)
    
```


Column {data-width=350}
-----------------------------------------------------------------------

### Chart B - Boxplot
Chart B includes a boxplot comparing the frequency of products ordered in the yogurt, fresh fruits, fresh vegetables, crackers, and ice cream ice aisles.  

```{r}
instacart %>% 
  janitor::clean_names()%>%
  filter(aisle %in% c("yogurt","fresh fruits","fresh vegetables", "crackers", "ice cream ice"))%>%
  group_by(aisle)%>%
  count(product_name)%>%
  plot_ly(y = ~n, color = ~aisle, type = "box", colors = "viridis")
```

### Chart C - Bar graph

Chart C contains a bar graph with that includes a random sample of 1000 rows from the instacart dataset. The number of times products were ordered from each aisle are displayed on this bar graph.
```{r}
instacart %>% 
  janitor::clean_names()%>%
  sample_n(1000)%>%
  count(aisle) %>% 
  mutate(aisle = fct_reorder(aisle, n)) %>% 
  plot_ly(x = ~aisle, y = ~n, color = ~aisle, type = "bar", colors = "viridis")
```